---
title: "Benchmark of results \"home6\" package"
author: "Toruniewska Joanna"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{benchmark}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

#Comparision of *mode()*

*Mode()* is R function. It returns the same results as *home6::mode()* function. 
```{r}

Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

a<-c(1,1,3,3,3,4,5,5,1,1)
b<-c(1:10,1,2,2,3,1,1)
c<-c(1,2,3,1,2,3,5,5,1,2,1,1:20, 1,0,2,5)
d<-c(1:10,10,NA)
e<-c(1:10,1:100,NA,1:50)
```
```{r}
system.time( replicate(10000, home6::mode(a) ) )
system.time( replicate(10000, Mode(a) ) )

system.time( replicate(10000, home6::mode(b) ) )
system.time( replicate(10000, Mode(b) ) )

system.time( replicate(10000, home6::mode(c) ) )
system.time( replicate(10000, Mode(c) ) )

system.time( replicate(10000, home6::mode(d) ) )
system.time( replicate(10000, Mode(d) ) )

system.time( replicate(10000, home6::mode(e) ) )
system.time( replicate(10000, Mode(e) ) )
```

We can see that *Mode()* (R) function is faster than *home6::mode()* (c++) function.

#Comparision of *simplify2array()*


The *base::simplify2array()* is the build-in R function, the *home6::simplify2array()* mimim it behaviour.

```{r}
a<-list(c(1,2,3), c(1,2,8))
b<-list(c(1:100), c(1:100))
c<-list(c(1,2,3), c(1,2,8),c(1,2,3), c(1,2,8),c(1,2,3), c(1,2,8),c(1,2,3), c(1,2,8),c(1,2,3), c(1,2,8),c(1,2,3), c(1,2,8),c(1,2,3), c(1,2,8),c(1,2,3), c(1,2,8) )
d<-lapply(c(1:10), function(x) {c(1:10)} )

```
```{r}
system.time( replicate(10000, home6::simplify2array(a) ) )
system.time( replicate(10000, base::simplify2array(a) ) )

system.time( replicate(10000, home6::simplify2array(b) ) )
system.time( replicate(10000, base::simplify2array(b) ) ) 

system.time( replicate(10000, home6::simplify2array( c)))
system.time( replicate(10000, base::simplify2array(c)))

system.time( replicate(10000, home6::simplify2array(d) ) )
system.time( replicate(10000, base::simplify2array(d) ) )
```

We can see that *home6::simplify2array* function is a little bit faster than *base::simplify2array* function.

#Comparision of *ass()*
```{r}
library(combinat)
Ass<-function(x){
  m<-t(combn(2*x,2))
  size<-length(m[,1])
  out<-matrix(0,nrow = size,ncol=2*x);
  for(y in c(1:size)){
    out[y,][m[y,]]<-c(1,1)
  }
  return(out)
}
a<-2
b<-5
c<-7

```
```{r}
system.time( replicate(1000, home6::ass(a) ) )
system.time( replicate(1000, Ass(a) ) )

system.time( replicate(1000, home6::ass(b) ) )
system.time( replicate(1000, Ass(b) ) ) 

system.time( replicate(1000, home6::ass( c)))
system.time( replicate(1000, Ass(c)))
```

We can see that *home6::ass()* function is a little bit faster than *Ass()* function for small *n*.
